oolong: An R package for validating  automated content analysis tools

### 2020-11-12 paper/paper.rmd
paper ORCID correction

---
title: 'oolong: An R package for validating  automated content analysis tools'
tags:
  - R
  - text analysis
  - topic model
  - sentiment analysis
  - validation
authors:
  - name: Chung-hong Chan
    orcid: 0000-0003-0872-7098
    affiliation: 1
  - name: Marius Sältzer
    orcid: 0000-0002-8604-4666
    affiliation: 1
affiliations:
 - name: Mannheimer Zentrum für Europäische Sozialforschung, Universität Mannheim
   index: 1
citation_author: Chan & Sältzer.
date: 15 October 2020
year: 2020
bibliography: paper.bib
output: rticles::joss_article
csl: apa.csl
journal: JOSS
---

>>>>

---
title: 'oolong: An R package for validating  automated content analysis tools'
tags:
  - R
  - text analysis
  - topic model
  - sentiment analysis
  - validation
authors:
  - name: Chung-hong Chan
    orcid: 0000-0002-6232-7530
    affiliation: 1
  - name: Marius Sältzer
    orcid: 0000-0002-8604-4666
    affiliation: 1
affiliations:
 - name: Mannheimer Zentrum für Europäische Sozialforschung, Universität Mannheim
   index: 1
citation_author: Chan & Sältzer.
date: 15 October 2020
year: 2020
bibliography: paper.bib
output: rticles::joss_article
csl: apa.csl
journal: JOSS
---
